Effects of Tunable Hydrophobicity on the Collective Hydrodynamics of Janus Particles under Flows

### 2023-02-23 doc/PRF2022/PRF_main.tex
peter revised a figure and its caption

>>>>

\begin{figure}[t]
\begin{center}
  \includegraphics[height=0.3\textheight]{ChangeLengthForce.pdf}
\end{center}
\begin{caption}{\label{fig:PramChange}
When the force parameters are tuned in the same percentage change, a linear proportional relationship between changes (square symbol) and the critical shear rates $\dot\gamma^*$ is shown in numerical results. The same adjustment in length parameters give a nearly linear trend with an inverse proportional relationship between changes (triangle symbol) and the critical shear rates.}
\end{caption}
\end{figure}

To further examine the contest between shear and head-tail attraction, we found that a 5\% and 10\% relative increases in the parameters $\gamma$ and
$M$ resulted in 4.29\% and 8.57\% relative increases in critial shear rate $\dot\gamma$, from 0.14 to 0.146 and 0.14 to 0.152, respectively. 
A proportional relationship is observed as the parameters decrease and it is shown in Figure~\ref{fig:PramChange}.
Moreover, Figure~\ref{fig:PramChange} also shows that 5\% and 10\% decreases in the particle radius c, screening length $\rho$ and repulsion distance $\rho_0$ gave 5.71\%  and 7.14\% increase in $\dot\gamma$ from 0.14 to 0.148 and 0.14 to 0.15.
In addition, 5\% and 10\% increases in length parameters gave 11.43\% and 18.57\% decrease in critical shear rate $\dot\gamma$.
The overall result provides another evidence that a different hydrophobicity suggests a dissimilar rheology and dynamics viscosity from the suspended vesicle experiments.
